---
title: "Initial Korean covid 19"
author: "Anicia Friend"
date: "2025-05-08"
output: 
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS~ARM

```{r}
basiccNN<- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basiccNN +geom_point()  +ggtitle("SIMS vs ARM")
```

The scatterplot of SIMS versus ARM shows an upward trend, indicating that as ARM increases, SIMS tends to increase as well.  

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential Results

```{r}
model1<- lm(SIMS~ARM,data=data)
summary.lm(model1)
```


### Target Dataframe

```{r}
target<-data.frame(ARM=90,GRIP=90)
```

```{r}
predict(model1,target,interval=c("prediction"))
```


```{r}
predict(model1,target,interval=c("confidence"))
```

### Linear fit Model 1


```{r}
basiccNN +geom_point()  +ggtitle("SIMS vs ARM") +geom_smooth(method=lm)
```


### Model2: SIMS~GRIP

```{r}
basiccNN2<- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basiccNN2 +geom_point()  +ggtitle("SIMS vs GRIP")
```

The relationship is positive, as the plot slopes upward to the right.  

### Numerical Results 2 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation between SIMS and GRIP is less than the correlation between SIMS and ARM.  

### Inferential Results 2

```{r}
model2<- lm(SIMS~GRIP,data=data)
summary.lm(model2)
```


```{r}
predict(model2,target,interval=c("prediction"))
```


```{r}
predict(model2,target,interval=c("confidence"))
```



The adjusted R squared form SIMS vs ARM is bigger than SIMS vs GRIP. 


```{r}
basiccNN2 +geom_point()  +ggtitle("SIMS vs GRIP") +geom_smooth(method=lm)
```

### Model3 SIMS~ARM+GRIP


```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)
```

### Inferential Results Model 3


```{r}
model3<- lm(SIMS~GRIP,data=data)
summary.lm(model3)
```

Our eqation is SIMS= -5.43387 +0.03731*ARM +0.2447*GRIP. That is the line in 3D space. 

```{r}
predict(model3,target,interval=c("prediction"))
```


```{r}
predict(model3,target,interval=c("confidence"))
```

The prediction interval for model3 is -2.2 to 2.4, and the confidence interval is -0.23 to 0.48. 

### ANOVA test for model1 and model3


```{r}
anova(model1,model3)
```


```{r}
anova(model2,model3)
```

```{r}
anova(model1,model2)
```


Model 1 is nested within Model 3, and Model 2 is also nested within Model 3. Because the models are nested, we can use an ANOVA test to compare them. The results show low p-values, indicating significant differences. However, if the models were not nested, the ANOVA test would not be appropriate.

